
---
layout: default
title: Guided Practice 8.1
---

# Guided Practice for 8.1: Sequences

## Overview

A sequence of numbers is an ordered list of numbers. In this section we move from continuous functions to discrete functions and determine what convergence means for sequences.

## Learning objectives

__Basic objectives__: Each student is responsible for gaining proficiency with each of these tasks _prior_ to engaging in class discussions, through the use of the learning resources (below) and through the working of exercises (also below).

- Define and give examples of sequences.
- Use a function to obtain a sequence.

__Advanced objectives__: The following objectives are the subject of class discussion and further work; they should be mastered by each student _during_ and _following_ class discussions.

- Determine whether a sequence converges or diverges using graphical and algebraic methods.
- Define convergence of a sequence.

## Learning resources

To gain proficiency in the learning objectives, use the following resources. You may include other resources if you wish, in addition to or in replacement of the following.

__Textbook__: In _Active Calculus_, read Section 8.1. Make sure to read actively, working through examples and activities as you go.

__Video__: Watch the following videos.

- [Quick Recap - Sequences](https://www.youtube.com/watch?v=kQYKcvtPjE0&t=0s&index=66&list=PL9bIjQJDwfGtewW75Nw7PnGNSkfqwAm3v) (4:42)
- [Finding a Formula for the nth term](https://www.youtube.com/watch?v=PiacUzL39zM&t=0s&index=68&list=PL9bIjQJDwfGtewW75Nw7PnGNSkfqwAm3v) (5:03)
- [Limits of Sequences](https://www.youtube.com/watch?v=WQTxhzaLblc&t=0s&index=67&list=PL9bIjQJDwfGtewW75Nw7PnGNSkfqwAm3v) (4:52)
- [Convergence of a Sequence](https://www.youtube.com/watch?v=eDnghUrg36o&t=0s&index=69&list=PL9bIjQJDwfGtewW75Nw7PnGNSkfqwAm3v) (5:47)


## Activities

The following activity is to be done _during_ and _following_ your reading and viewing of the resources. Go to [student.desmos.com](https://student.desmos.com/?prepopulateCode=9q5fc) and enter your name in the format `Last, First`. For example, I would enter my name as `Ballif, Serge`. Complete each part of the activity. Some of these problems will require you to work them out on paper before entering your answer. Practice producing high quality work so that your work is readable and meaningful. You will receive a mark of __Pass__ if each item response shows a good-faith effort to be right and is submitted prior to the deadline. __Remember to use the Piazza discussion board to ask about any questions you have.__
