\documentclass{ximera}

\input{preamble.tex} %% we can turn off input when making a master document

\prerequisites{none}

\title{Introduction}

\begin{document}

\begin{abstract}
We introduce the class structure.
\end{abstract}
\maketitle

For each day of class you will complete a pre-class activity that will prepare you for the day's content. Class time will be devoted to practicing techniques and skills and following up on questions. There will be very little time spent on lecturing during the course so it is important for you to come prepared by completing the pre-class assignments. Also, don't miss class because there is no way to make up the points on the in-class activities.

Each section comes with learning objectives. Please take these seriously, as they set the bar for the level of content that you should understand when you come to class and when you finish class. 

The pre-class activities make it so that we get to spend class time working on problems that would normally be assigned as homework. This makes the homework assignments shorter and more focused. The pre-class work is designed to baby-step you through some new concepts. Hints and example videos are provided. Our intention is that you should be able to get a perfect score on all of the pre-class activities. If something is tripping you up, then please ask about it on the class discussion board.

You will have access to each of the pre-class activities throughout the semester. However, after the due date the credit will be reduced by 50\%. Don't fall behind.

The pre-class activities will typically take less than an hour while the homework will take one to two hours. Please plan accordingly.


\begin{question}
Which statement below is false?
    \begin{multipleChoice}
      \choice{Your grade for each pre-class activities will drop 50\% if you complete it after class starts.}
      \choice{You should plan for about 3 hours of study outside of class for each hour in class.}
      \choice{Pre-class activities will prepare you for class.}
      \choice{If you have any questions you should post the question on the class discussion board.}
      \choice[correct]{It is ok to miss class if you have a tutor who can help you get caught up.}
    \end{multipleChoice}
    \begin{hint}
    Don't miss class. 
    \end{hint}
    \begin{hint}
    There is no way to make up the points missed on the in-class activities. 
    \end{hint}
\end{question}

Click on ``Next Activity'' to proceed to move on.

\end{document}
